Estimating migration rates for iteroparous species using kinship pairs found between populations

### 2021-12-20 latex/ms.tex
add text for CV and required sample size

Proposed estimators are based on the observed number of kinship pairs. Their expected number is linearly determined by the number of pairwise comparison (Eqs.~\ref{HS-2-1}-\ref{HS-2-2} and \ref{PO-2-1}-\ref{PO-2-2}), providing guidance for a sample size to ensure the condition that at least one or more kinship pairs can be found. The conditions are given by
\begin{align}
n_{\rm O, 1} n_{\rm O, 2} &> \frac{ N_{2} } { 4m },
\label{RS-1}
\end{align}
and
\begin{align}
n_{\rm O, 1} n_{\rm P, 2} &> \frac{ N_{2} } { 2m }.
\label{RS-2}
\end{align}
Roughly speaking, required sample size to ensure above conditions is that $n>\sqrt{N_2}$, where $n = n_{\rm O, 1}=n_{\rm O, 2}=n_{\rm P, 2}$. It should be noted that very tiny $m$, which dramatically increases the required sample size, produces significant genetic differences between two populations. In such a case, there are several methods to estimate migration rate by population genetics technique; alternatively, we focus the situation of moderate/large migration rate, which leads little genetic differences between two populations (see details in {\bf Results and Discussion} section).

@@

\section{Results and Discussion}\label{sec3}

>>>>

Proposed estimators are based on the observed number of kinship pairs. Their expected number is linearly determined by the number of pairwise comparison (Eqs.~\ref{HS-2-1}-\ref{HS-2-2} and \ref{PO-2-1}-\ref{PO-2-2}), providing guidance for a sample size to ensure the condition that at least one or more kinship pairs can be found. The conditions are given by
\begin{align}
n_{\rm O, 1} n_{\rm O, 2} &> \frac{ N_{2} } { 4m },
\label{RS-1}
\end{align}
and
\begin{align}
n_{\rm O, 1} n_{\rm P, 2} &> \frac{ N_{2} } { 2m }.
\label{RS-2}
\end{align}
Roughly speaking, required sample size to ensure above conditions is that $n>\sqrt{N_2}$, where $n = n_{\rm O, 1}=n_{\rm O, 2}=n_{\rm P, 2}$. It should be noted that very tiny $m$, which dramatically increases the required sample size, produces significant genetic differences between two populations. In such a case, there are several methods to estimate migration rate by population genetics technique; alternatively, we focus the situation of moderate/large migration rate, which leads little genetic differences between two populations (see details in {\bf Discussion} section).

Other guidance for the required sample size is obtained by an approximate lower bound on the CV (coefficient of variation) of $M_1$ or $m_1$, which is defined by $1/\sqrt{H_{\rm HS, bet}}$. For example, to achieve a 30\% CV, the target of $H_{\rm HS, bet}$ is more than 10, providing the required sample size when population parameters are given (e.g., $N_1$, $N_2$ and $M$). Similarly, the CV of $M_2$ or $m_2$, defined by $1/\sqrt{H_{\rm PO, bet}}$, provides the required sample size for estimating $M_2$ or $m_2$.

@@

\section{Results}\label{sec3}

\section{Discussion}\label{sec4}
